Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
Better phrasing.
Some stuff about browser extension.

@@

@@

We are running a paid instance of the web app on App Engine for use by the public.
The cost for bandwidth on App Engine is \$0.12 per gigabyte,
with one gigabyte free each day.
The total cost has so far been \$1.11, with bills of
\$0.09 in March,
\$0.73 in April,
and \$0.29 in May through May~12.

>>>>

% Avoid line breaks in program names.
\def\meekclient{\mbox{meek-client}}
\def\meekserver{\mbox{meek-server}}

@@

We implemented two versions of a browser extension, one for Firefox and one for Chrome.
They both work similarly: they open a TCP port on localhost,
await instructions from \meekclient\ on what HTTP requests to make,
issue the requests, and return the responses.

Figure~\ref{fig:browser-architecture} shows the interaction of components
on the user's computer.
Rather than starting \meekclient\ directly, the tor
process starts a helper process that starts both \meekclient\
and a headless browser instance.
The headless browser runs our extension in a separate
process and separate browser profile from the browser the
user interacts with; the two browser instances share no state.
\meekclient\ is configured to issue its requests through the browser extension;
in this configuration, the headless browser is the only thing that ever touches the network.

The use of a browser extension offers benefits beyond its TLS signature.
We inherit other characteristics of the browser:
how often it resolves DNS names,
its connection reuse,
and HTTP keepalive behavior.
The Firefox extension has special usability advantages because the Tor Browser Bundle
uses a modified Firefox.
We can include a small extension in the browser bundle and reuse the existing
Firefox executable without increasing the download size of the bundle much,
and without requiring users to separately configure a browser to run the extension.

@@

We are running a paid instance of the web app on App Engine for use by the public.
The cost for bandwidth on App Engine is \$0.12 per gigabyte,
with one gigabyte free each day.
The total cost has so far been \$1.11, with bills of
\$0.09 in March,
\$0.73 in April,
and \$0.29 in the first half of May.
